Probing the inner kpc of massive lens galaxies with ALMA: Can the central images of strong lenses be detected?

### 2014-10-24 ms.tex
modifying fig 1: model density profile

\begin{figure}
\begin{center}
\centering
\includegraphics[trim= 0 0 5 6, clip, width=0.45\textwidth]{figures/f_01.eps}
\centering
\end{center}
\caption{ illustration of the central image in 2 cases: 
\label{f:f2}}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\centering
\includegraphics[trim= 0 0 5 6, clip, width=0.45\textwidth]{figures/f_01.eps}
\centering
\end{center}
\caption{ Model density profiles. The black dashed line shows the dark matter component, with a slope of 0.1, consistent with a projected NFW at the innermost regions. the grey dashed curves show cored-sersic five fits to stellar light profiles of massive galaxies from Ferrarese 2006. The red solid curve shows our cored-powerlaw model that we use to approximate this stellar component. The solid black line shows the total matter density (dark plus stellar) of our model. 
\label{f:f2}}
\end{figure}
